\blue{Numerical Investigation of Multi-Fluid Flows through Dual Saturated-Unsaturated Porous Media - change the title to something close to the main topic of the manuscript ... something with viscous flow instability or viscous fingering)}

### 2017-02-20 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
keep on updating

\subsection{Model Validation}
Initially a case to demonstrate the model validation against experiments is described in fig. \ref{fig:square}. A simple square shape formation consisted of$4$ square regions that each one has $2$ values of different permeabilities (K is represented by the blue and red shaded square areas). The aspect ratio of the domain is $1$ and is fully saturated with fluid $2$. At the upper and lower sides of the domain no-slip boundary condition is applied, meaning there is no mass transport in and out of the domain. The left hand side of the domain is defined as the inlet for fluid $1$ with a velocity of $u=1$ while the right hand side is the outlet and pressure is set to $0$. Fluid $1$ across the left hand side of the formation is trying to displace the existing fluid $2$. What can been seen here is a cross flow case as the flow passes through different regions and develops. The front start to collapse at the first half of the lenght D (D:distance) of the domain ($x= \frac{1}{2} D)$.

\begin{figure}
\begin{center}
\subfigure[Initial and boundary conditions]{\includegraphics[width=0.75\textwidth]{./Pics/2b2_P1DGP2.pdf}\label{a}}
\subfigure[Plots of velocity magnitude, pressure and phase volume fraction]{\includegraphics[width=0.6\textwidth]{./Pics/2b2_P1DGP2_plot.pdf}\label{b}}
\caption{This is the first test-case of a square region with four subregions of constant permeabilities K. The mesh is unstructured but fixed and on average there are 5000 elements. Fluid $1$ is introduced from the right hand side at a constant velocity of u = 1, while as the flow progress the velocity magnitude drops to zero close to the outlet. This is a cross flow example based on the experimental work of \citet{evans_1994}. The main finger desrcibes the cross flow and starts to dies out during the transition from one permeability zone to another and as it approaches closer to the right boundary.}
\label{fig:square}
\end{center}
\end{figure}

@@

Fluid $1$ is again injected across the left hand side of the formation. Mobility ratios of different values will be introduced and compared. As the flow is developed the initial uniform front collapses start forming fingers, areas where the flow is developed faster than the rest of the main body of the flow. The new unstructured and adaptive mesh with the $P_{n}DG-P_{n+1}$ element type is used in order to capture the flow development. In fig. \ref{fig:simple_case} the simple case of a domain with uniform permeability is displayed.

\begin{figure}[h]
\begin{center}
\includegraphics[width=0.6\textwidth]{./Pics1/phase_vol_frac_unif_perm.pdf}
\caption{This is the simple case where the initially piston shape front is collapsing and starts forming fingers, in a domain with uniform permeability.}
\label{fig:simple_case}
\end{center}
\end{figure}

>>>>

\subsection{Model Validation}

The set of test-cases that we are going to illustrate starts with an elementary case in an homogeneous domain. The aim of this test-case is to verify that the numerical model is actually working in different simulation/scenarios starting from the basic ones. But one step before that, is to verify the existence of cross flow in the following domain as this is defined in fig. \ref{fig:simple_case}. Fluid $1$ is introduced on the  across the left hand side of the formation. Later different mobility ratios and different regions of various permeabilities will be introduced, but for now only few of these initial and boundary conditions will be applied.

\begin{figure}[h]
\begin{center}
\includegraphics[width=0.75\textwidth]{./Pics/phase_vol_frac_uni_perm_1.pdf}
\caption{This is the simple case where the initially piston shape front is collapsing and starts forming fingers, in a domain with uniform permeability.}
\label{fig:simple_case}
\end{center}
\end{figure}

One more case to demonstrate the model validation against experiments is described in fig. \ref{fig:square}. A square shape formation consisted of$4$ square regions that each one has $2$ values of different permeabilities (K is represented by the blue and red shaded square areas). The aspect ratio of the domain is $1$ and is fully saturated with fluid $2$. At the upper and lower sides of the domain no-slip boundary condition is applied, meaning there is no mass transport in and out of the domain. The left hand side of the domain is defined as the inlet for fluid $1$ with a velocity of $u=1$ while the right hand side is the outlet and pressure is set to $0$. Fluid $1$ across the left hand side of the formation is trying to displace the existing fluid $2$. What can been seen here is a cross flow case as the flow passes through different regions and develops. The front start to collapse at the first half of the lenght D (D:distance) of the domain ($x= \frac{1}{2} D)$.

\begin{figure}
\begin{center}
\subfigure[Initial and boundary conditions]{\includegraphics[width=0.65\textwidth]{./Pics/2b2_P1DGP2.pdf}\label{a}}
\subfigure[Plots of velocity magnitude, pressure and phase volume fraction]{\includegraphics[width=0.6\textwidth]{./Pics/2b2_P1DGP2_plot.pdf}\label{b}}
\caption{This is the first test-case of a square region with four subregions of constant permeabilities K. The mesh is unstructured but fixed and on average there are 5000 elements. Fluid $1$ is introduced from the right hand side at a constant velocity of u = 1, while as the flow progress the velocity magnitude drops to zero close to the outlet. This is a cross flow example based on the experimental work of \citet{evans_1994}. The main finger desrcibes the cross flow and starts to dies out during the transition from one permeability zone to another and as it approaches closer to the right boundary.}
\label{fig:square}
\end{center}
\end{figure}

@@
